Handling String-Number Conversion in String Constraint Solving

### 2019-11-11 evaluation.tex
added a note about the validator to the experimental section

We compare \textsf{z3-Trau} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}. We do not compare with Sloth \cite{sloth} since it does not support length constraints. We present data on two benchmark groups (see Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}) that demonstrate two points. First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories. Second, we show that our tool is competitive on well-known benchmarks that can be effectively handled by other existing solvers. All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test. The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulae. Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported invalid answer or crashed.

>>>>

We compare \textsf{z3-Trau} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}. We do not compare with Sloth \cite{sloth} since it does not support length constraints. We present data on two benchmark groups that demonstrate two points. First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories. Second, we show that our tool is competitive on well-known benchmarks that can be effectively handled by other existing solvers. The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulae. Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported incorrect answer or crashed.

Occasionally, during the experiments, there was a case where a solver reported a different answer to a test than the other solvers. To decide which solver reported the incorrect answer, we have developed our own validator. Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test. The modified test is re-evaluated by solvers and if the solvers decide that the modified test is satisfiable, the answer of the solvers that originally reported unsat is evaluated as incorrect.
